% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projets}{\faLaptop}

\begin{projects}
	\project
	{Nomination for Bachelor of the year by Accenture}{Summer 2016}
	{}
	{The bachelor project I was a part of was among the top 8 finalists out of thousands of other STEM bachelor projects in Accenture’s Bachelor of The Year 2016.}
	{}
				
	\project
	{hotMap - Bachelor project}{Spring 2016}
	{\website{https://daisy-git.cs.aau.dk/zanderdk/hotMap}{https://daisy-git.cs.aau.dk/zanderdk/hotMap}}
	{This project was a part of a larger project, aSTEP, involving around 40 people. aSTEPis a service for applications to share and store locations and map data that also includes map matching and user management.
	
	I was a part of a smaller group of 5 people that developed an application that used the aSTEP core. We had contact with the security personnel on Skanderborg Festival, the second largest festival in Denmark, who were interested due to a series of problematic events at concerts from 2013 through 2015. In collaboration with them, we developed an open-source system that uses WiFi triangulation through smartphones WiFi modules combined with specific event attendance information utilising kernel density estimation to detect crowd conditions and hazardous situations on festivals and large events to better aid security personnel detect, prevent and defuse dangerous and uncomfortable situations.}
	{Scala, JavaScript, HTML/CSS, Graded 12/A}
	
	\project
	{AHA - Automated Home Automation}{Autumn 2015}
	{\github{Hutli/AHA}}
	{A system for imitating users’ behavioural patterns using hidden Markov Models and embedded devices. We proposed a solution for imitating users’ behavioural patterns.Embedded  devices  were  used  to  observe  the  state  of  the  problem  domain.  Hidden Markov models were created, based on the history of states, and the Viterbi algorithm was used to predict a user’s behaviour. The solution could learn simple patterns and imitate appropriate actions within a reasonable time span.}
	{Java, Arduino C, Graded 10/B+}
	
	\project
	{TLDR}{Spring 2015}
	{\github{Hutli/TLDR}}
	{A high-level, modular, functional first, domain-specific programming language intended for natural and social scientists to model objects and interactions between objects in concurrent real-world systems with a full small-step semantics formal specification and formal syntax in BCNF form.}
	{F\#, LLVM, Graded 10/B+}
	
	\project
	{TLDR}{Autumn 2014}
	{\github{Hutli/openPlaylist}}
	{A triple-platform mobile application where users can vote for tracks at bars, private events or public spaces, to create a playlist fitting for the crowd. The project was developed in collaboration with the bar Fabrikken in central Aalborg, where it was tested and implemented. Usability tests with potential users were conducted and analysed.}
	{C\#, Xamarin, Cross-platform mobile, Graded: 12/A}

\end{projects}